cvx-flats

### 2020-04-20 neurips-20/cvx-flats.tex
notes

\begin{definition}[Flat]
	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
\end{definition}

@@

\begin{theorem}\label{thm:cvx-flats}
	Suppose we are given a property $\gamma$.
	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
\end{theorem}
\begin{proof}[Proof intuition]
	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.

	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e. $L$ also indirectly elicits $\gamma$.
	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.

	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n]$ such that $\sum_y p_y x_y = \vec 0$.

	\jessiet{This next paragraph is mostly me spelling it out for myself}
	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
	We also claim that $F \cap \simplex \subseteq \gamma_r$.
	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.

>>>>

\begin{definition}[Flat]
	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
  \raft{Would suggest defining a bit more formally after, like ``In other words, $F\subseteq \reals^d$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.  Then you can define the dimension of $F$ easily as $d$, assuming the matrix is full rank}
\end{definition}

@@

\begin{theorem}\label{thm:cvx-flats}
	Suppose we are given a property $\gamma$.
  \raft{Made logic more direct}
	If, for any $p \in \simplex$, and $r\in\gamma(p)$,
	there is no $(n - d - 1)$-dimensional flat $F$ satisfying both $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}[Proof intuition]
	We prove the contrapositive: if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
  \raft{Nice way to start.}

	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e., $L$ indirectly elicits $\gamma$.
	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}\raft{It's a good exercise to look up the necessary results in e.g. Rockafellar (let me know if you don't have a copy; I can send a PDF).  Note that $L(\cdot,y)$ is defined on all of $\reals^d$ for all $y$, which is key.  I'd recommend spelling this out in 2-3 sentences.}.

	Observe that the Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n]$ such that $\sum_y p_y x_y = \vec 0$.
  \raft{State the dimensions of $W$}

	\jessiet{This next paragraph is mostly me spelling it out for myself}
  \raft{Don't understand; this is necessary to complete the proof!  (So good thing you have it.)}
	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
  \raft{Justify the dimension.  Hint: $F$ contains $\vec 0$.  You'll probably want to define some $F'$ by adding a certain something to $W$ -- check out the FSD paper.}
	We also claim that $F \cap \simplex \subseteq \gamma_r$.
	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
